Performances Code

### 2019-01-29 Scripts/performances.rmd
aggregated results from prcurves for all balancing techniques

```{r}
#10kb
prall <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/all/RFE/prcurve.rds")
prdist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/oc/RFE/prcurve.rds")
prop <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/op/RFE/prcurve.rds")

prall_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/all/RFE/prcurve.rds")
prdist_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/oc/RFE/prcurve.rds")
prop_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/op/RFE/prcurve.rds")

prdata_10kb <- rbind.data.frame(prall$curve,
                                prdist$curve,
                                prop$curve,
                                proc$curve,
                                prall_k562$curve,
                                prdist_k562$curve,
                                prop_k562$curve,
                                proc_k562$curve)
names(prdata_10kb) <- c("Recall", "Precision", "Threshold")
prdata_10kb$Predictor <- c(rep("All", dim(prall$curve)[1]),
                           rep("Distance", dim(prdist$curve)[1]),
                           rep("OP", dim(prop$curve)[1]),
                           rep("OC", dim(proc$curve)[1]),
                           rep("All", dim(prall_k562$curve)[1]),
                           rep("Distance", dim(prdist_k562$curve)[1]),
                           rep("OP", dim(prop_k562$curve)[1]),
                           rep("OC", dim(proc_k562$curve)[1]))
prdata_10kb$CL <- c(rep("GM12878", (dim(prall$curve)[1]+
                                      dim(prdist$curve)[1]+
                                      dim(prop$curve)[1]+
                                      dim(proc$curve)[1])),
                    rep("K562", (dim(prall_k562$curve)[1]+
                                      dim(prdist_k562$curve)[1]+
                                      dim(prop_k562$curve)[1]+
                                      dim(proc_k562$curve)[1])))
prdata_10kb$Predictor <- factor(prdata_10kb$Predictor)
prdata_10kb$CL <- factor(prdata_10kb$CL)

prplot_10kb <- ggplot(prdata_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
  geom_line(size=.75)+
  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
  scale_color_discrete(name = "Predictor Type") +
  theme_minimal()+
  theme_bw()

#25kb
prall <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/all/RFE/prcurve.rds")
prdist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/oc/RFE/prcurve.rds")
prop <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/op/RFE/prcurve.rds")

prall_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/all/RFE/prcurve.rds")
prdist_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/oc/RFE/prcurve.rds")
prop_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/op/RFE/prcurve.rds")

prdata_25kb <- rbind.data.frame(prall$curve,
                                prdist$curve,
                                prop$curve,
                                proc$curve,
                                prall_k562$curve,
                                prdist_k562$curve,
                                prop_k562$curve,
                                proc_k562$curve)
names(prdata_25kb) <- c("Recall", "Precision", "Threshold")
prdata_25kb$Predictor <- c(rep("All", dim(prall$curve)[1]),
                           rep("Distance", dim(prdist$curve)[1]),
                           rep("OP", dim(prop$curve)[1]),
                           rep("OC", dim(proc$curve)[1]),
                           rep("All", dim(prall_k562$curve)[1]),
                           rep("Distance", dim(prdist_k562$curve)[1]),
                           rep("OP", dim(prop_k562$curve)[1]),
                           rep("OC", dim(proc_k562$curve)[1]))
prdata_25kb$CL <- c(rep("GM12878", (dim(prall$curve)[1]+
                                      dim(prdist$curve)[1]+
                                      dim(prop$curve)[1]+
                                      dim(proc$curve)[1])),
                    rep("K562", (dim(prall_k562$curve)[1]+
                                      dim(prdist_k562$curve)[1]+
                                      dim(prop_k562$curve)[1]+
                                      dim(proc_k562$curve)[1])))
prdata_25kb$Predictor <- factor(prdata_25kb$Predictor)
prdata_25kb$CL <- factor(prdata_25kb$CL)

prplot_25kb <- ggplot(prdata_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
  geom_line(size=.75)+
  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
  scale_color_discrete(name = "Predictor Type") +
  theme_minimal()+
  theme_bw()

#50kb
prall <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/all/RFE/prcurve.rds")
prdist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/oc/RFE/prcurve.rds")
prop <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/op/RFE/prcurve.rds")

prall_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/all/RFE/prcurve.rds")
prdist_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/oc/RFE/prcurve.rds")
prop_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/op/RFE/prcurve.rds")

prdata_50kb <- rbind.data.frame(prall$curve,
                                prdist$curve,
                                prop$curve,
                                proc$curve,
                                prall_k562$curve,
                                prdist_k562$curve,
                                prop_k562$curve,
                                proc_k562$curve)
names(prdata_50kb) <- c("Recall", "Precision", "Threshold")
prdata_50kb$Predictor <- c(rep("All", dim(prall$curve)[1]),
                           rep("Distance", dim(prdist$curve)[1]),
                           rep("OP", dim(prop$curve)[1]),
                           rep("OC", dim(proc$curve)[1]),
                           rep("All", dim(prall_k562$curve)[1]),
                           rep("Distance", dim(prdist_k562$curve)[1]),
                           rep("OP", dim(prop_k562$curve)[1]),
                           rep("OC", dim(proc_k562$curve)[1]))
prdata_50kb$CL <- c(rep("GM12878", (dim(prall$curve)[1]+
                                      dim(prdist$curve)[1]+
                                      dim(prop$curve)[1]+
                                      dim(proc$curve)[1])),
                    rep("K562", (dim(prall_k562$curve)[1]+
                                      dim(prdist_k562$curve)[1]+
                                      dim(prop_k562$curve)[1]+
                                      dim(proc_k562$curve)[1])))
prdata_50kb$Predictor <- factor(prdata_50kb$Predictor)
prdata_50kb$CL <- factor(prdata_50kb$CL)

prplot_50kb <- ggplot(prdata_50kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
  geom_line(size=.75)+
  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
  scale_color_discrete(name = "Predictor Type") +
  theme_minimal()+
  theme_bw()

#100kb
prall <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/all/RFE/prcurve.rds")
prdist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/oc/RFE/prcurve.rds")
prop <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/op/RFE/prcurve.rds")

prall_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/all/RFE/prcurve.rds")
prdist_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/oc/RFE/prcurve.rds")
prop_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/op/RFE/prcurve.rds")

prdata_100kb <- rbind.data.frame(prall$curve,
                                prdist$curve,
                                prop$curve,
                                proc$curve,
                                prall_k562$curve,
                                prdist_k562$curve,
                                prop_k562$curve,
                                proc_k562$curve)
names(prdata_100kb) <- c("Recall", "Precision", "Threshold")
prdata_100kb$Predictor <- c(rep("All", dim(prall$curve)[1]),
                           rep("Distance", dim(prdist$curve)[1]),
                           rep("OP", dim(prop$curve)[1]),
                           rep("OC", dim(proc$curve)[1]),
                           rep("All", dim(prall_k562$curve)[1]),
                           rep("Distance", dim(prdist_k562$curve)[1]),
                           rep("OP", dim(prop_k562$curve)[1]),
                           rep("OC", dim(proc_k562$curve)[1]))
prdata_100kb$CL <- c(rep("GM12878", (dim(prall$curve)[1]+
                                      dim(prdist$curve)[1]+
                                      dim(prop$curve)[1]+
                                      dim(proc$curve)[1])),
                    rep("K562", (dim(prall_k562$curve)[1]+
                                      dim(prdist_k562$curve)[1]+
                                      dim(prop_k562$curve)[1]+
                                      dim(proc_k562$curve)[1])))
prdata_100kb$Predictor <- factor(prdata_100kb$Predictor)
prdata_100kb$CL <- factor(prdata_100kb$CL)

prplot_100kb <- ggplot(prdata_100kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
  geom_line(size=.75)+
  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
  scale_color_discrete(name = "Predictor Type") +
  theme_minimal()+
  theme_bw()

ggarrange(prplot_25kb, prplot_50kb, prplot_100kb,
          nrow=2,ncol=2,
          common.legend = TRUE, legend = "right")
```

>>>>

```{r}
#10kb
##None
prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/all/RFE/prcurve.rds")
prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/oc/RFE/prcurve.rds")
prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/op/RFE/prcurve.rds")

prall_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/all/RFE/prcurve.rds")
prdist_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/oc/RFE/prcurve.rds")
prop_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/op/RFE/prcurve.rds")

prdata_None_10kb <- rbind.data.frame(prall_None$curve,
                                prdist_None$curve,
                                prop_None$curve,
                                proc_None$curve,
                                prall_None_k562$curve,
                                prdist_None_k562$curve,
                                prop_None_k562$curve,
                                proc_None_k562$curve)
names(prdata_None_10kb) <- c("Recall", "Precision", "Threshold")
prdata_None_10kb$Predictor <- c(rep("All", dim(prall_None$curve)[1]),
                           rep("Distance", dim(prdist_None$curve)[1]),
                           rep("OP", dim(prop_None$curve)[1]),
                           rep("OC", dim(proc_None$curve)[1]),
                           rep("All", dim(prall_None_k562$curve)[1]),
                           rep("Distance", dim(prdist_None_k562$curve)[1]),
                           rep("OP", dim(prop_None_k562$curve)[1]),
                           rep("OC", dim(proc_None_k562$curve)[1]))
prdata_None_10kb$CL <- c(rep("GM12878", (dim(prall_None$curve)[1]+
                                      dim(prdist_None$curve)[1]+
                                      dim(prop_None$curve)[1]+
                                      dim(proc_None$curve)[1])),
                    rep("K562", (dim(prall_None_k562$curve)[1]+
                                      dim(prdist_None_k562$curve)[1]+
                                      dim(prop_None_k562$curve)[1]+
                                      dim(proc_None_k562$curve)[1])))
prdata_None_10kb$Predictor <- factor(prdata_None_10kb$Predictor)
prdata_None_10kb$CL <- factor(prdata_None_10kb$CL)

prplot_None_10kb <- ggplot(prdata_None_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
  geom_line(size=.75)+
  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
  scale_color_discrete(name = "Predictor Type") +
  theme_minimal()+
  theme_bw()

##RUS
prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/all/RFE/prcurve.rds")
prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/oc/RFE/prcurve.rds")
prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/op/RFE/prcurve.rds")

prall_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/all/RFE/prcurve.rds")
prdist_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
proc_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/oc/RFE/prcurve.rds")
prop_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/op/RFE/prcurve.rds")

prdata_RUS_10kb <- rbind.data.frame(prall_RUS$curve,
                                prdist_RUS$curve,
                                prop_RUS$curve,
                                proc_RUS$curve,
                                prall_RUS_k562$curve,
                                prdist_RUS_k562$curve,
                                prop_RUS_k562$curve,
                                proc_RUS_k562$curve)
names(prdata_RUS_10kb) <- c("Recall", "Precision", "Threshold")
prdata_RUS_10kb$Predictor <- c(rep("All", dim(prall_RUS$curve)[1]),
                           rep("Distance", dim(prdist_RUS$curve)[1]),
                           rep("OP", dim(prop_RUS$curve)[1]),
                           rep("OC", dim(proc_RUS$curve)[1]),
                           rep("All", dim(prall_RUS_k562$curve)[1]),
                           rep("Distance", dim(prdist_RUS_k562$curve)[1]),
                           rep("OP", dim(prop_RUS_k562$curve)[1]),
                           rep("OC", dim(proc_RUS_k562$curve)[1]))
prdata_RUS_10kb$CL <- c(rep("GM12878", (dim(prall_RUS$curve)[1]+
                                      dim(prdist_RUS$curve)[1]+
                                      dim(prop_RUS$curve)[1]+
                                      dim(proc_RUS$curve)[1])),
                    rep("K562", (dim(prall_RUS_k562$curve)[1]+
                                      dim(prdist_RUS_k562$curve)[1]+
                                      dim(prop_RUS_k562$curve)[1]+
                                      dim(proc_RUS_k562$curve)[1])))
prdata_RUS_10kb$Predictor <- factor(prdata_RUS_10kb$Predictor)
prdata_RUS_10kb$CL <- factor(prdata_RUS_10kb$CL)

prplot_RUS_10kb <- ggplot(prdata_RUS_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
  geom_line(size=.75)+
  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
  scale_color_discrete(name = "Predictor Type") +
  theme_minimal()+
  theme_bw()

##ROS
prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/all/RFE/prcurve.rds")
prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/oc/RFE/prcurve.rds")
prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/op/RFE/prcurve.rds")

prall_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/all/RFE/prcurve.rds")
prdist_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
proc_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/oc/RFE/prcurve.rds")
prop_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/op/RFE/prcurve.rds")

prdata_ROS_10kb <- rbind.data.frame(prall_ROS$curve,
                                prdist_ROS$curve,
                                prop_ROS$curve,
                                proc_ROS$curve,
                                prall_ROS_k562$curve,
                                prdist_ROS_k562$curve,
                                prop_ROS_k562$curve,
                                proc_ROS_k562$curve)
names(prdata_ROS_10kb) <- c("Recall", "Precision", "Threshold")
prdata_ROS_10kb$Predictor <- c(rep("All", dim(prall_ROS$curve)[1]),
                           rep("Distance", dim(prdist_ROS$curve)[1]),
                           rep("OP", dim(prop_ROS$curve)[1]),
                           rep("OC", dim(proc_ROS$curve)[1]),
                           rep("All", dim(prall_ROS_k562$curve)[1]),
                           rep("Distance", dim(prdist_ROS_k562$curve)[1]),
                           rep("OP", dim(prop_ROS_k562$curve)[1]),
                           rep("OC", dim(proc_ROS_k562$curve)[1]))
prdata_ROS_10kb$CL <- c(rep("GM12878", (dim(prall_ROS$curve)[1]+
                                      dim(prdist_ROS$curve)[1]+
                                      dim(prop_ROS$curve)[1]+
                                      dim(proc_ROS$curve)[1])),
                    rep("K562", (dim(prall_ROS_k562$curve)[1]+
                                      dim(prdist_ROS_k562$curve)[1]+
                                      dim(prop_ROS_k562$curve)[1]+
                                      dim(proc_ROS_k562$curve)[1])))
prdata_ROS_10kb$Predictor <- factor(prdata_ROS_10kb$Predictor)
prdata_ROS_10kb$CL <- factor(prdata_ROS_10kb$CL)

prplot_ROS_10kb <- ggplot(prdata_ROS_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
  geom_line(size=.75)+
  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
  scale_color_discrete(name = "Predictor Type") +
  theme_minimal()+
  theme_bw()

##SMOTE
prall_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
prdist_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
proc_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
prop_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/op/RFE/prcurve.rds")

prall_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")
prdist_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")
proc_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/oc/RFE/prcurve.rds")
prop_SMOTE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/op/RFE/prcurve.rds")

prdata_SMOTE_10kb <- rbind.data.frame(prall_SMOTE$curve,
                                prdist_SMOTE$curve,
                                prop_SMOTE$curve,
                                proc_SMOTE$curve,
                                prall_SMOTE_k562$curve,
                                prdist_SMOTE_k562$curve,
                                prop_SMOTE_k562$curve,
                                proc_SMOTE_k562$curve)
names(prdata_SMOTE_10kb) <- c("Recall", "Precision", "Threshold")
prdata_SMOTE_10kb$Predictor <- c(rep("All", dim(prall_SMOTE$curve)[1]),
                           rep("Distance", dim(prdist_SMOTE$curve)[1]),
                           rep("OP", dim(prop_SMOTE$curve)[1]),
                           rep("OC", dim(proc_SMOTE$curve)[1]),
                           rep("All", dim(prall_SMOTE_k562$curve)[1]),
                           rep("Distance", dim(prdist_SMOTE_k562$curve)[1]),
                           rep("OP", dim(prop_SMOTE_k562$curve)[1]),
                           rep("OC", dim(proc_SMOTE_k562$curve)[1]))
prdata_SMOTE_10kb$CL <- c(rep("GM12878", (dim(prall_SMOTE$curve)[1]+
                                      dim(prdist_SMOTE$curve)[1]+
                                      dim(prop_SMOTE$curve)[1]+
                                      dim(proc_SMOTE$curve)[1])),
                    rep("K562", (dim(prall_SMOTE_k562$curve)[1]+
                                      dim(prdist_SMOTE_k562$curve)[1]+
                                      dim(prop_SMOTE_k562$curve)[1]+
                                      dim(proc_SMOTE_k562$curve)[1])))
prdata_SMOTE_10kb$Predictor <- factor(prdata_SMOTE_10kb$Predictor)
prdata_SMOTE_10kb$CL <- factor(prdata_SMOTE_10kb$CL)

prplot_SMOTE_10kb <- ggplot(prdata_SMOTE_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
  geom_line(size=.75)+
  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
  scale_color_discrete(name = "Predictor Type") +
  theme_minimal()+
  theme_bw()

##ROSE
prall_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")
prdist_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
proc_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
prop_ROSE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/op/RFE/prcurve.rds")

prall_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")
prdist_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")
proc_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/oc/RFE/prcurve.rds")
prop_ROSE_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/op/RFE/prcurve.rds")

prdata_ROSE_10kb <- rbind.data.frame(prall_ROSE$curve,
                                prdist_ROSE$curve,
                                prop_ROSE$curve,
                                proc_ROSE$curve,
                                prall_ROSE_k562$curve,
                                prdist_ROSE_k562$curve,
                                prop_ROSE_k562$curve,
                                proc_ROSE_k562$curve)
names(prdata_ROSE_10kb) <- c("Recall", "Precision", "Threshold")
prdata_ROSE_10kb$Predictor <- c(rep("All", dim(prall_ROSE$curve)[1]),
                           rep("Distance", dim(prdist_ROSE$curve)[1]),
                           rep("OP", dim(prop_ROSE$curve)[1]),
                           rep("OC", dim(proc_ROSE$curve)[1]),
                           rep("All", dim(prall_ROSE_k562$curve)[1]),
                           rep("Distance", dim(prdist_ROSE_k562$curve)[1]),
                           rep("OP", dim(prop_ROSE_k562$curve)[1]),
                           rep("OC", dim(proc_ROSE_k562$curve)[1]))
prdata_ROSE_10kb$CL <- c(rep("GM12878", (dim(prall_ROSE$curve)[1]+
                                      dim(prdist_ROSE$curve)[1]+
                                      dim(prop_ROSE$curve)[1]+
                                      dim(proc_ROSE$curve)[1])),
                    rep("K562", (dim(prall_ROSE_k562$curve)[1]+
                                      dim(prdist_ROSE_k562$curve)[1]+
                                      dim(prop_ROSE_k562$curve)[1]+
                                      dim(proc_ROSE_k562$curve)[1])))
prdata_ROSE_10kb$Predictor <- factor(prdata_ROSE_10kb$Predictor)
prdata_ROSE_10kb$CL <- factor(prdata_ROSE_10kb$CL)

prplot_ROSE_10kb <- ggplot(prdata_ROSE_10kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
  geom_line(size=.75)+
  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
  scale_color_discrete(name = "Predictor Type") +
  theme_minimal()+
  theme_bw()

##Collecting 10kb plots
ggarrange(prplot_None_10kb,
          prplot_RUS_10kb,
          prplot_ROS_10kb,
          prplot_SMOTE_10kb,
          prplot_ROSE_10kb,
          nrow=3,ncol=2,
          common.legend = TRUE, legend = "right")

#######################################################################################

#25kb
##None
prall_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/all/RFE/prcurve.rds")
prdist_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/oc/RFE/prcurve.rds")
prop_None <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/op/RFE/prcurve.rds")

prall_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/all/RFE/prcurve.rds")
prdist_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/prcurve.rds")
proc_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/oc/RFE/prcurve.rds")
prop_None_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/op/RFE/prcurve.rds")

prdata_None_25kb <- rbind.data.frame(prall_None$curve,
                                prdist_None$curve,
                                prop_None$curve,
                                proc_None$curve,
                                prall_None_k562$curve,
                                prdist_None_k562$curve,
                                prop_None_k562$curve,
                                proc_None_k562$curve)
names(prdata_None_25kb) <- c("Recall", "Precision", "Threshold")
prdata_None_25kb$Predictor <- c(rep("All", dim(prall_None$curve)[1]),
                           rep("Distance", dim(prdist_None$curve)[1]),
                           rep("OP", dim(prop_None$curve)[1]),
                           rep("OC", dim(proc_None$curve)[1]),
                           rep("All", dim(prall_None_k562$curve)[1]),
                           rep("Distance", dim(prdist_None_k562$curve)[1]),
                           rep("OP", dim(prop_None_k562$curve)[1]),
                           rep("OC", dim(proc_None_k562$curve)[1]))
prdata_None_25kb$CL <- c(rep("GM12878", (dim(prall_None$curve)[1]+
                                      dim(prdist_None$curve)[1]+
                                      dim(prop_None$curve)[1]+
                                      dim(proc_None$curve)[1])),
                    rep("K562", (dim(prall_None_k562$curve)[1]+
                                      dim(prdist_None_k562$curve)[1]+
                                      dim(prop_None_k562$curve)[1]+
                                      dim(proc_None_k562$curve)[1])))
prdata_None_25kb$Predictor <- factor(prdata_None_25kb$Predictor)
prdata_None_25kb$CL <- factor(prdata_None_25kb$CL)

prplot_None_25kb <- ggplot(prdata_None_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
  geom_line(size=.75)+
  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
  scale_color_discrete(name = "Predictor Type") +
  theme_minimal()+
  theme_bw()

##RUS
prall_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/all/RFE/prcurve.rds")
prdist_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
proc_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/oc/RFE/prcurve.rds")
prop_RUS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/op/RFE/prcurve.rds")

prall_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/all/RFE/prcurve.rds")
prdist_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")
proc_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/oc/RFE/prcurve.rds")
prop_RUS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/op/RFE/prcurve.rds")

prdata_RUS_25kb <- rbind.data.frame(prall_RUS$curve,
                                prdist_RUS$curve,
                                prop_RUS$curve,
                                proc_RUS$curve,
                                prall_RUS_k562$curve,
                                prdist_RUS_k562$curve,
                                prop_RUS_k562$curve,
                                proc_RUS_k562$curve)
names(prdata_RUS_25kb) <- c("Recall", "Precision", "Threshold")
prdata_RUS_25kb$Predictor <- c(rep("All", dim(prall_RUS$curve)[1]),
                           rep("Distance", dim(prdist_RUS$curve)[1]),
                           rep("OP", dim(prop_RUS$curve)[1]),
                           rep("OC", dim(proc_RUS$curve)[1]),
                           rep("All", dim(prall_RUS_k562$curve)[1]),
                           rep("Distance", dim(prdist_RUS_k562$curve)[1]),
                           rep("OP", dim(prop_RUS_k562$curve)[1]),
                           rep("OC", dim(proc_RUS_k562$curve)[1]))
prdata_RUS_25kb$CL <- c(rep("GM12878", (dim(prall_RUS$curve)[1]+
                                      dim(prdist_RUS$curve)[1]+
                                      dim(prop_RUS$curve)[1]+
                                      dim(proc_RUS$curve)[1])),
                    rep("K562", (dim(prall_RUS_k562$curve)[1]+
                                      dim(prdist_RUS_k562$curve)[1]+
                                      dim(prop_RUS_k562$curve)[1]+
                                      dim(proc_RUS_k562$curve)[1])))
prdata_RUS_25kb$Predictor <- factor(prdata_RUS_25kb$Predictor)
prdata_RUS_25kb$CL <- factor(prdata_RUS_25kb$CL)

prplot_RUS_25kb <- ggplot(prdata_RUS_25kb, aes(x=Recall, y=Precision, color=Predictor, linetype=CL)) +
  geom_line(size=.75)+
  scale_linetype_manual(name=("Cell Line"), values=c("solid", "dashed"))+
  scale_color_discrete(name = "Predictor Type") +
  theme_minimal()+
  theme_bw()

##ROS
prall_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/all/RFE/prcurve.rds")
prdist_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
proc_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/oc/RFE/prcurve.rds")
prop_ROS <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/op/RFE/prcurve.rds")

prall_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/all/RFE/prcurve.rds")
prdist_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")
proc_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/oc/RFE/prcurve.rds")
prop_ROS_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/op/RFE/prcurve.rds")
